\begin{thebibliography}{10}
\addcontentsline{toc}{chapter}{Bibliografia}

\bibitem{WaszakModel}Waszak, M. R.: 
\emph{Modelling The Benchmark Active Control Technology Windtunnel Model for Application to Flutter Suppression}, NASA Langley Research Center, Hampton, Virginia, 1996.

\bibitem{WaszakRobust}Waszak, M. R.: 
\emph{Robust Multivariable Flutter Suppression for the Benchmark Active Control Technology (BACT) Wind-Tunnel Model}, NASA Langley Research Center, Hampton, Virginia, 1997.

\bibitem{WaszakFlutter}Waszak, M. R.; Srinathkumar, S.: 
\emph{Flutter Suppression for the Active Flexible Wing: Control System Design and Experimental Validation}, American Institute of Aeronautics and Astronautics, 1991.

\bibitem{Padfield}Padfield, G. D.: 
\emph{Dynamika lotu œmig³owców, Wydawnictwo Komunikacji i ³¹cznoœci}, 1998.

\bibitem{ADS}
\emph{Aeronautical Design Standard (ADS) 33E - Handling Qualities for Military Helicopters}
, US Army, 2000.

\bibitem{Robust}Magni, J.; Bennani, S.; Terlow J.: 
\emph{Robust flight control: a design challenge. Springer-Verlag}
, Berlin, 1997.

\bibitem{Handbook}Levine, W.: 
\emph{The Control Handbook}
, CRC press, 1996.

\bibitem{PadfieldCameron}Padfield, G. D.; Cameron, N.: 
\emph{Handling Qualities Degradation in Tilt-Rotor Aircraft Following Flight Control System Failure}.

\bibitem{SLA}B. Manimala, G. D. Padfield and D. Walker:
\emph{Load Alleviation in Tilt Rotor Aircraft through Active Control; Modelling and Control Concepts}, The Aeronautical Journal, 2004.

\bibitem{FBW}Schmitt, V. R.; Morris, J.W.; Jenney, G.D.: 
\emph{Fly-by-wire, a historical design perspective}
, Warrendale: Society of Automotive Engineers,1998.

\bibitem{MacLean}MacLean, D.: 
\emph{Automatic flight control systems}
, Prentice Hall, 1990.

\bibitem{Cooper}Cooper G. E.; Harper R. P. Jr.: 
\emph{The Use of Pilot Ratings in the Evaluation of Aircraft Hanling Qualities}
, AGARD report 567, 1969.

\bibitem{Wysocki}Wysocki, M.: 
\emph{Sterowanie wielowymiarowe. Projektowanie liniowych uk³adów stacjonarnych w przestrzeni stanu}
, Oficyna Wydawnicza Politechniki Rzeszowskiej, 2004.

\bibitem{FlightInt}
\emph{Flight international}
, nr 5.08.2003.

\bibitem{Garimella} Garimella, S.:
\emph{Actuator Modeling and Control for a Three Degrees of Freedom Differential Thrust Control Testbed}
, Master Thesis, Ohio University, 2007.
\url{http://etd.ohiolink.edu/view.cgi?acc_num=ohiou1195164411}

%\bibitem{Nelson}Nelson, R. C.: 
%\emph{Solutions Manual to Accompany Flight Stability and Automatic Control}
%,WCB/McGraw-Hill, 1998.

\end{thebibliography}
